Cover Letter

### 2017-12-28 paper/cover_letter.tex
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

To show the relevance of the use cases, we re-wrote Section~{\S}V-B to
highlight examples from HPC and cloud workloads that would benefit from using
Cudele. For HPC we focus on user home directories used for experiments and for
the cloud we focus on the Hadoop and Spark runtimes (as suggested by Reviewer
2). To connect the problematic use cases to Cudele, we added \textbf{Cudele
setup} headers in Section~{\S}V-B to show which subtree semantics accomodate
these workloads in the global namespace.  By showing these setups, we hope to
demonstrate that different applications can use a file system in parallel with
different consistency/durability semantics.  Although we do not actually run
the workloads on our prototype, hopefully our changes show how the use cases,
and the synthetic benchmarks we used to represent them, are indeed relevant to
parallel and distributed computing.

@@

>>>>

To show the relevance of the use cases, we re-wrote Section~{\S}V-B to
highlight examples from HPC and cloud workloads that would benefit from using
Cudele. For HPC we focus on user home directories used for experiments and for
the cloud we focus on the Hadoop and Spark runtimes (as suggested by Reviewer
2). To connect the problematic use cases to Cudele, we added \textbf{Cudele
setup} headers in Section~{\S}V-B to show which subtree semantics accommodate
these workloads in the global namespace.  By showing these setups, we hope to
demonstrate that different applications can use a file system in parallel with
different consistency/durability semantics.  Although we do not actually run
the workloads on our prototype, hopefully our changes show how the use cases,
and the synthetic benchmarks we used to represent them, are indeed relevant to
parallel and distributed computing.

@@

We also clarified confusing terminology in a footnote in Section~{\S}I: we use
the term administrator to refer to a person that configures subtrees and client
to refer to a storage client or application that interacts with the metadata
server. We avoid using the term ``user" except when referring to end-users that
interact with home directories in a file system or the Hadoop/Spark runtime
itself.

### 2017-12-28 paper/sections/0_abstract.tex
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show 8\(\times\) speedup and can scale to 2\(\times\) as many clients when
compared to our baseline system.

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets \oldcomment{clients}\newcomment{administrators} specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing administrators to optimize subtrees over time and
space for different workloads.  We confirm the performance benefits of
techniques presented in related work but also explore new
consistency/durability metadata designs, all integrated over the same storage
system.  By custom fitting a subtree to a create-heavy application, we show
similar speedups to related work \newcomment{but more importantly, our
prototype can custom fit subtrees in the same namespace to applications common
in large data centers, such as checkpoint-restart (91.7\(\times\), user home
directories (within a 0.03 standard deviation from optimal), and
\oldcomment{clients}\newcomment{users} checking for partial results (only a 2\%
overhead).}  \oldcomment{ and can scale to 2\(\times\) as many clients when
compared to our baseline system.}

### 2017-12-28 paper/sections/1_introduction.tex
paper: wordsmithing
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current hardware and software trends; for example, HPC architectures are
transitioning from complex storage stacks with burst buffer, file system,
object store, and tape tiers to more simplified stacks with just a burst buffer
and object store~\cite{bent:login16-hpc-trends}. These types of trends put
pressure on data access because more requests end up hitting the same layer and
latencies cannot be hidden while data migrates across tiers.

@@

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients can relax consistency on their
subtree (HDFS) or decouple the subtree and move it locally (BatchFS, RAMDisk).
Decoupled subtrees can relax durability for even better performance.
}\label{fig:subtree-policies} \end{figure}

@@

Our prototype system, Cudele, achieves this by exposing ``mechanisms" that
users combine to specify their preferred semantics.  Cudele supports 3 forms
of consistency (invisible, weak, and strong) and 3 degrees of durability (none,
local, and global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. We make the following contributions:

@@

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users navigate
  the trade-offs of different metadata protocols on the same storage system.

@@

  \item A prototype that lets users custom fit subtrees to applications
  dynamically.

@@

\oldcomment{The last contribution lays the groundwork for future work on our
prototype. It is more scalable than the current practice of mounting different
storage systems in a global namespace because there is no need to provision
dedicated storage clusters to applications or move data between these systems.
For example, the results of a Hadoop job do not need to be migrated into a Ceph
file system (CephFS) for other processing; instead the user can change the
semantics of the HDFS subtree into a CephFS subtree.  This may cause
metadata/data movement to make things strongly consistent again but this is
superior to moving all data across file system boundaries. Our prototype
enables studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.}

% Results
The results in this paper pave the way for such a system and confirm the
assertions of ``clean-state" research of decoupled namespaces; specifically
that these techniques drastically improve performance.  We go a step further by
quantifying the costs of merging updates (3.37\(\times\) slow down) and
maintaining durability (\(2.4\times\) slow down).  In our prototype,
\newcomment{we also show how to assign subtree semantics for certain
applications such as checkpoint-restart (\(91.7\times\) speedup if consistency
is fully relaxed), user home directories (within a 0.03 standard deviation from
optimal), and clients checking for partial results (only a 2\% overhead).}
\oldcomment{we get an 8\(\times\) speedup and can scale to twice as many
clients when we assign a more relaxed form of consistency and durability to a
subtree with a create-heavy workload.}  We use Ceph as a prototyping platform
because it is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

>>>>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client\footnote{In this paper, ``client"
is a storage client or application that interacts with the metadata server,
``administrator" is a system administrator that configures the storage, and
``end-users" interact with the file system, via home directories or runtimes.}}
is unreasonable. This problem is exacerbated by current hardware and software
trends: parallel runtimes like Hadoop and Spark use storage systems to
implement important scheduling and timing semantics, and  \oldcomment{; for
example, } HPC architectures are transitioning from complex storage stacks with
burst buffer, file system, object store, and tape tiers to more simplified
stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put pressure on
data access because more requests from different nodes end up hitting the same
layer in parallel and latencies cannot be hidden while data migrates across
tiers.

@@

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients \oldcomment{can} relax consistency on their
subtree (HDFS) or decouple the subtree and move it locally (BatchFS, RAMDisk).
Decoupled subtrees can relax durability for even better performance.
}\label{fig:subtree-policies} \end{figure}

@@

Our prototype system, Cudele, achieves this by exposing ``mechanisms" that
\oldcomment{users}\newcomment{administrators} combine to specify their
preferred semantics.  Cudele supports 3 forms of consistency (invisible, weak,
and strong) and 3 degrees of durability (none, local, and global) giving the
\oldcomment{user}\newcomment{administrator} a wide range of policies and
optimizations that can be custom fit to an application. We make the following
contributions:

@@

  \item A framework and API for assigning consistency/durability policies to
  subtrees in the file system namespace; this lets
  \oldcomment{users}\newcomment{administrators} navigate the trade-offs of
  different metadata protocols on the same storage system.

@@

  \item A prototype that lets \oldcomment{users}\newcomment{administrators}
  custom fit subtrees to applications dynamically.

@@

\oldcomment{The last contribution lays the groundwork for future work on our
prototype. It is more scalable than the current practice of mounting different
storage systems in a global namespace because there is no need to provision
dedicated storage clusters to applications or move data between these systems.
For example, the results of a Hadoop job do not need to be migrated into a Ceph
file system (CephFS) for other processing; instead the
\oldcomment{users}\newcomment{administrator} can change the semantics of the
HDFS subtree into a CephFS subtree.  This may cause metadata/data movement to
make things strongly consistent again but this is superior to moving all data
across file system boundaries. Our prototype enables studies that adjust these
semantics over {\it time and space}, where subtrees can change their semantics
and migrate around the cluster without ever moving the data they reference.}

% Results
The results in this paper pave the way for such a system and confirm the
assertions of ``clean-state" research of decoupled namespaces; specifically
that these techniques drastically improve performance.  We go a step further by
quantifying the costs of merging updates (3.37\(\times\) slowdown) and
maintaining durability (\(2.4\times\) slowdown).  In our prototype,
\newcomment{we also show how to assign subtree semantics for certain
applications such as checkpoint-restart (\(91.7\times\) speedup if consistency
is fully relaxed), user home directories (within a 0.03 standard deviation from
optimal), and end-users checking for partial results (only a 2\% overhead).}
\oldcomment{we get an 8\(\times\) speedup and can scale to twice as many
clients when we assign a more relaxed form of consistency and durability to a
subtree with a create-heavy workload.}  We use Ceph as a prototyping platform
because it is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

### 2017-12-28 paper/sections/3_posix_overheads.tex
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
Create-heavy workloads (such as \texttt{untar}) incur the highest disk,
network, and CPU utilization because of the consistency and durability demands
of CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.1\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}

  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results are normalized to 1 client that creates 100K files in isolation.  (a)
shows the effect of journaling metadata updates; ``segment(s)" is the number
of journal segments dispatched to disk at once. (b) shows the slowdown when
another client interferes by creating files in all directories and (c)
highlights the cause: }\oldcomment{The overhead of durability and strong
consistency in CephFS. (a) shows the effect of different journal segment sizes,
which are streamed into the object store for fault tolerance. (b) and (c) show
that} when another client ``interferes", capabilities are revoked and metadata
servers do more work.} \label{fig:overhead}

\end{figure*}

% what is durability
While durability is not specified by POSIX IO, users expect that files they
create or modify survive failures.  We define three types of durability:
global, local, and none.  Global durability means that the client or server can
fail at any time and metadata will not be lost because it is ``safe" ({\it
i.e.} striped or replicated across a cluster). Local durability means that
metadata can be lost if the client or server stays down after a failure. None
means that metadata is volatile and that the system provides no guarantees when
clients or servers fail.  None is different than local durability because
regardless of the type of failure, metadata will be lost when components die in a
None configuration.

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
the consistency and durability demands of CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1.15\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results in (a) and (b)  are normalized to 1 client that creates 100K files in
isolation.  (a) shows the effect of journaling metadata updates; ``segment(s)"
is the number of journal segments dispatched to disk at once. (b) shows the
slowdown when another client interferes by creating files in all directories
and (c) highlights the cause: }\oldcomment{The overhead of durability and
strong consistency in CephFS. (a) shows the effect of different journal segment
sizes, which are streamed into the object store for fault tolerance. (b) and
(c) show that} when another client ``interferes", capabilities are revoked and
metadata servers do more work.} \label{fig:overhead}
\end{figure*}

% what is durability
While durability is not specified by POSIX IO,
\oldcomment{users}\newcomment{administrators} expect that files they create or
modify survive failures.  We define three types of durability: global, local,
and none.  Global durability means that the client or server can fail at any
time and metadata will not be lost because it is ``safe" ({\it i.e.} striped or
replicated across a cluster). Local durability means that metadata can be lost
if the client or server stays down after a failure. None means that metadata is
volatile and that the system provides no guarantees when clients or servers
fail.  None is different than local durability because regardless of the type
of failure, metadata will be lost when components die in a None configuration.

### 2017-12-28 paper/sections/4_methodology.tex
paper: final version
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In this section we describe our API and framework that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct \textbf{policies}.
These policies are assigned to subtrees and they dictate how the file system
should handle operations within that subtree.  Below, we describe the
mechanisms (which are \underline{underlined}), the policies, and the API for assigning
policies to subtrees.

@@

% describe table
The spectrum of consistency and durability guarantees that users can construct
is shown in Table~\ref{table:spectrum}. The columns are the different
consistency semantics and the rows cover the spectrum of durability guarantees.
For consistency: ``invisible" means the system does not handle merging updates
into a global namespace and it is assumed that middleware or the application
manages consistency lazily; ``weak" merges updates at some time in the future
({\it e.g.}, when the system has time, when the number of updates reaches a
certain threshold, when the client is done writing, etc.); and updates in
``strong" consistency are seen immediately by all clients. For durability,
``none" means that updates are volatile and will be lost on a failure. Stronger
guarantees are made with ``local", which means updates will be retained if the
client node recovers and reads the updates from local storage, and ``global",
where all updates are always recoverable.

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability~\footnote{This is the
normal case.  IndexFS also has bulk merge which would transition the system
into ``weak consistency"}; DeltaFS uses ``invisible" consistency and ``local"
durability and BatchFS uses ``weak" consistency and ``local" durability. These
systems have other features that could push them into different semantics but
we assign labels here based on the points emphasized in the papers.  To compose
the mechanisms users inject which mechanisms to run and which to use in
parallel using a domain specific language.  Although we can achieve all
permutations of the different guarantees in Table~\ref{table:spectrum}, not all
of them make sense. For example, it makes little sense to do \texttt{append
client journal+RPCs} since both mechanisms do the same thing or
\texttt{stream+local persist} since ``global" durability is stronger and has more
overhead than ``local" durability. The cost of each mechanism and the semantics
described above are quantified in Sections~\S\ref{sec:microbenchmarks}
and~\S\ref{sec:use-case-1}.

>>>>

In this section we describe our API and framework that lets
\oldcomment{users}\newcomment{administrators} assign consistency and durability
semantics to subtrees in the global namespace. A \textbf{mechanism} is an
abstraction and basic building block for constructing consistency and
durability guarantees. Cudele exposes these mechanisms and the
\oldcomment{users}\newcomment{administrator} composes them together to
construct \textbf{policies}.  These policies are assigned to subtrees and they
dictate how the file system should handle operations within that subtree.
Below, we describe the mechanisms (which are \underline{underlined}), the
policies, and the API for assigning policies to subtrees.

@@

% describe table
The spectrum of consistency and durability guarantees that
\oldcomment{users}\newcomment{administrators} can construct is shown in
Table~\ref{table:spectrum}. The columns are the different consistency semantics
and the rows cover the spectrum of durability guarantees.  For consistency:
``invisible" means the system does not handle merging updates into a global
namespace and it is assumed that middleware or the application manages
consistency lazily; ``weak" merges updates at some time in the future ({\it
e.g.}, when the system has time, when the number of updates reaches a certain
threshold, when the client is done writing, etc.); and updates in ``strong"
consistency are seen immediately by all clients. For durability, ``none" means
that updates are volatile and will be lost on a failure. Stronger guarantees
are made with ``local", which means updates will be retained if the client node
recovers and reads the updates from local storage, and ``global", where all
updates are always recoverable.

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability\footnote{This is the
normal case.  IndexFS also has bulk merge which would transition the system
into ``weak consistency"}; DeltaFS uses ``invisible" consistency and ``local"
durability and BatchFS uses ``weak" consistency and ``local" durability. These
systems have other features that could push them into different semantics but
we assign labels here based on the points emphasized in the papers.  To compose
the mechanisms \oldcomment{users}\newcomment{administrators} inject which
mechanisms to run and which to use in parallel using a domain specific
language.  Although we can achieve all permutations of the different guarantees
in Table~\ref{table:spectrum}, not all of them make sense. For example, it
makes little sense to do \texttt{append client journal+RPCs} since both
mechanisms do the same thing or \texttt{stream+local persist} since ``global"
durability is stronger and has more overhead than ``local" durability. The cost
of each mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

### 2017-12-28 paper/sections/6_results.tex
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques themselves against
other file systems, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace\oldcomment{, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application}. \newcomment{These techniques have already proven to be
effective and scalable in systems that specialize an entire namespace according
to a single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS), so our
evaluation explores the behavior of the consistency/durability mechanisms and
their effect with and without isolation.}

@@

Next we show how Cudele can be programmed to block interfering
clients\oldcomment{ using the same problematic workload from
Figure~\ref{fig:overhead-b}. In this workload, c}\newcomment{, which lets
applications control isolation to get better and more reliable performance.}
Clients create 100K files in their own directories while another client
interferes by creating \oldcomment{more}\newcomment{1000} files in each
directory. \oldcomment{This}\newcomment{The workload} introduces false sharing
and the metadata server revokes capabilities on directories touched by the
interfering client. While HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.  \newcomment{ In the cloud, Spark and
Hadoop stacks use HDFS, which lets users ignore this type of consistency completely
by letting interfering clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}.}

@@

The final use case shows how the API gives users fine-grained control of the
consistency semantics \newcomment{to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Spark and Hadoop write to temporary
files, renames them when complete, and creates a ``DONE" file to indicate to
the runtime that the task did not fail and should not be re-scheduled on
another node. \newcomment{Also, the browser interface lets users check the
progress by querying the file system and returning a \% of job complete
metric.}

% Does this implementation need to be described in the implementation?
\newcomment{\textbf{Cudele setup}: in this scenario, Cudele users will not see
the progress of decoupled namespaces since their updates are not globally
visible.  To provide the performance of decoupled namespaces and to help users
judge the progress of their jobs, Cudele clients have a ``namespace sync" that
sends batches of updates back to the global namespace at regular intervals.
We configure a subtree as a decoupled namespace with invisible consistency, local
durability, and partial updates enabled.}

@@

\newcomment{We have shown that our API and framework is an effective
abstraction for letting users custom fit subtrees to applications.  It is more
scalable than the current practice of mounting different storage systems in a
global namespace because there is no need to provision dedicated storage
clusters to applications or move data between these systems.  For example, the
results of a Hadoop job do not need to be migrated into a Ceph file system
(CephFS) for other processing; instead the user can change the semantics of the
HDFS subtree into a CephFS subtree.  This may cause metadata/data movement to
make things strongly consistent again but this is superior to moving all data
across file system boundaries. Our prototype enables studies that adjust these
semantics over {\it time and space}, where subtrees can change their semantics
and migrate around the cluster without ever moving the data they reference.}

>>>>

Cudele lets \oldcomment{users}\newcomment{administrators} construct
consistency/durability guarantees using well-established research techniques
from other systems; so instead of evaluating the scalability and performance of
the techniques themselves against other file systems, we show that (1) the
mechanisms we propose are useful for constructing semantics used by real
systems, (2) the techniques can work side-by-side in the same
namespace\oldcomment{, and (3) the combination of these techniques can help the
system scale further when subtrees are coupled to the correct type of
application}. \newcomment{These techniques have already proven to be effective
and scalable in systems that specialize an entire namespace according to a
single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS), so our
evaluation explores the behavior of the consistency/durability mechanisms and
their effect with and without isolation.}

@@

Next we show how Cudele can be programmed to block interfering
clients\oldcomment{ using the same problematic workload from
Figure~\ref{fig:overhead-b}. In this workload, c}\newcomment{, which lets
applications control isolation to get better and more reliable performance.}
Clients create 100K files in their own directories while another client
interferes by creating \oldcomment{more}\newcomment{1000} files in each
directory. \oldcomment{This}\newcomment{The workload} introduces false sharing
and the metadata server revokes capabilities on directories touched by the
interfering client. While HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.  \newcomment{ In the cloud, Spark and
Hadoop stacks use HDFS, which lets clients ignore this type of consistency completely
by letting interfering clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}.}

@@

The final use case shows how the API gives
\oldcomment{users}\newcomment{administrators} fine-grained control of the
consistency semantics \newcomment{to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Spark and Hadoop write to temporary
files, renames them when complete, and creates a ``DONE" file to indicate to
the runtime that the task did not fail and should not be re-scheduled on
another node. \newcomment{Also, the browser interface lets Hadoop/Spark users check the
progress by querying the file system and returning a \% of job complete
metric.}

% Does this implementation need to be described in the implementation?
\newcomment{\textbf{Cudele setup}: in this scenario, Cudele end-users will not see
the progress of decoupled namespaces since their updates are not globally
visible.  To provide the performance of decoupled namespaces and to help end-users
judge the progress of their jobs, Cudele clients have a ``namespace sync" that
sends batches of updates back to the global namespace at regular intervals.
We configure a subtree as a decoupled namespace with invisible consistency, local
durability, and partial updates enabled.}

@@

\newcomment{We have shown that our API and framework is an effective
abstraction for letting \oldcomment{users}\newcomment{administrators} custom
fit subtrees to applications.  It is more scalable than the current practice of
mounting different storage systems in a global namespace because there is no
need to provision dedicated storage clusters to applications or move data
between these systems.  For example, the results of a Hadoop job do not need to
be migrated into a Ceph file system (CephFS) for other processing; instead the
\oldcomment{user}\newcomment{administrator} can change the semantics of the HDFS
subtree into a CephFS subtree.  This may cause metadata/data movement to make
things strongly consistent again but this is superior to moving all data across
file system boundaries. Our prototype enables studies that adjust these
semantics over {\it time and space}, where subtrees can change their semantics
and migrate around the cluster without ever moving the data they reference.}

### 2017-12-28 paper/sections/7_conclusion.tex
paper: terminology, spark, scoping (#47, #36, #35)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Relaxing consistency/durability semantics in the file system is a double-edged
sword. While it performs and scales better, it alienates applications that rely
on strong consistency and durability. Mounting other systems to the global
namespace is convenient but wastes resources and incurs data movement.  Cudele
lets users assign consistency/durability guarantees to subtrees in the global
namespace, which can be custom fit to the application. Using Cudele, we show
how applications can co-exist and perform well in a global namespace and lay
the groundwork for new systems that dynamically change consistency/durability
guarantees to avoid provisioning dedicated storage clusters and moving large
amounts of data.

>>>>

Relaxing consistency/durability semantics in the file system is a double-edged
sword. While it performs and scales better, it alienates applications that rely
on strong consistency and durability. Mounting other systems to the global
namespace is convenient but wastes resources and incurs data movement.  Cudele
lets \oldcomment{users}\newcomment{administrators} assign
consistency/durability guarantees to subtrees in the global namespace, which
can be custom fit to the application. Using Cudele, we show how applications
can co-exist and perform well in a global namespace and lay the groundwork for
new systems that dynamically change consistency/durability guarantees to avoid
provisioning dedicated storage clusters and moving large amounts of data.
